\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
reworded feature description table

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{|p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}|}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D cartesian path traced by [link] in \tj{} w.r.t BFS path or between 3D Cartesian path traced by [link1] and [link2] in \tj{}\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path traced by [link] in \tj{} and the BFS path, or between 3D-cartesian-path traced by [link1] and [link2] in \tj{}\\
\hline
\end{tabular}
}
\caption{The complete list of computed trajectory features used for classification.}
\end{table}

>>>>

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{|p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}|}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D path of [link] w.r.t BFS path or between 3D paths of [link1] and [link2]\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path of [link] and the BFS path, or between paths of [link1] and [link2]\\
\hline
\end{tabular}
}
\caption{The complete list of computed trajectory features used for classification.}
\end{table}
